Ms 1

### 2017-07-26 ms1/ms1_display.Rmd
more streamlining

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)
import::from(tools, md5sum)

pctize = function(df, denom_name) {
  for (n_name in Filter(function(x) str_detect(x, '^n_'), names(df))) {
    pct_name = str_replace(n_name, '^n_', 'pct_')
    df[[pct_name]] = df[[n_name]] / df[[denom_name]] * 100
  }
  df
}
```

@@

```{r, eval=FALSE}
model_ci = function(df) {
  mutate(df, ci_range=1.96*std.error,
         ci_low=estimate-ci_range,
         ci_high=estimate+ci_range)
}

model_ci_cpkp = function(df) {
  model_ci(df) %>%
    mutate_at(vars(ci_range, ci_low, ci_high, estimate), function(x) x*1000) %>%
    rename(cpkp=estimate)
}

read_tsv('tables/tbl_cohort_model2.tsv') %>%
  filter(term=='year') %>%
  model_ci_cpkp() %>%
  kable

read_tsv('tables/tbl_cohort_model_abx.tsv') %>%
  filter(model %in% c('azithromycin', 'levofloxacin'), term=='year') %>%
  select(term, estimate, std.error, model) %>%
  model_ci_cpkp() %>%
  kable
```

# Summary of data

@@

```{r}
totals_dat = read_tsv('tables/totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, sd_age, mean_n_cc, sd_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west)

totals_dat %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1)) %>%
  mutate_at(vars(mean_n_cc, sd_age, sd_n_cc),
            function(x) round(x, digits=2)) %>% 
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

```{r}
trend_p = function(x) tidy(t.test(diff(x)))$p.value

totals_dat %>%
  gather('var', 'val', -year) %>%
  arrange(var, year, val) %>%
  group_by(var) %>%
  summarize(p=trend_p(val)) %>%
  mutate(adj.p=p.adjust(p, method='BH'),
         sig=if_else(adj.p<0.05, '*', '')) %>%
  kable
```

@@

```{r}
claims_by_abx = read_tsv('tables/claims_by_abx.tsv')

top_abx = claims_by_abx %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

top_abx_f = function(df) {
  totals = group_by(df, year) %>%
    summarize(cpkp=sum(cpkp)) %>%
    mutate(antibiotic='all')

  df %>%
    select(antibiotic, year, cpkp) %>%
    filter(antibiotic %in% top_abx) %>%
    bind_rows(totals) %>%
    mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))
}
```

```{r}
claims_by_abx %>%
  top_abx_f() %>%
  ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption')

claims_by_abx %>%
  filter(antibiotic %in% top_abx) %>%
  mutate(antibiotic=factor(antibiotic, levels=top_abx)) %>%
  ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3) +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption')

claims_by_abx %>%
  top_abx_f() %>%
  filter(year %in% c(2011, 2014)) %>%
  spread(year, cpkp) %>%
  mutate(pct_change=(`2014`-`2011`)/`2011`*100) %>%
  kable
```

@@

```{r}
read_tsv('tables/claims_by_sex.tsv') %>%
  select(sex, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-sex), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/claims_by_region.tsv') %>%
  select(region, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-region), round) %>%
  kable
```

@@

```{r}
read_tsv('tables/claims_by_race.tsv') %>%
  select(race, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-race), round) %>%
  kable
```

@@

```{r adjusted_changes, cache.extra=md5sum('tables/model_abx.tsv')}
x = read_tsv('tables/model_abx.tsv') %>%
  filter(model=='poisson', term=='year', antibiotic %in% top_abx) %>%
  arrange(estimate) %>%
  mutate(ci=1.96*std.error,
         pct_change=exp(estimate)-1,
         ci_low=exp(estimate-ci)-1,
         ci_high=exp(estimate+ci)-1) %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>% mutate(antibiotic=forcats::fct_inorder(antibiotic)) %>%
  mutate_if(is.numeric, function(x) x*100)

p = x %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  #geom_linerange(aes(x=antibiotic, ymin=0, ymax=cpkp_per_year)) +
  geom_linerange() +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  xlab('') +
  ylab('adjusted yearly change in claims per beneficiary per year') +
  #scale_y_continuous(limits=c(-16, 17), breaks=c(-15, -10, -5, 0, 5, 10, 15)) +
  theme_minimal()

show(p)
#ggsave('fig/fig_adjusted_changes.pdf', plot=p)

x %>% kable
```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(stringr, str_replace, str_detect)
library(forcats)
import::from(tools, md5sum)
```

@@

```{r abstract}
pctize = function(df, denom_name) {
  for (n_name in Filter(function(x) str_detect(x, '^n_'), names(df))) {
    pct_name = str_replace(n_name, '^n_', 'pct_')
    df[[pct_name]] = df[[n_name]] / df[[denom_name]] * 100
  }
  df
}

totals = read_tsv('tables/totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, sd_age, mean_n_cc, sd_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west)

claims_by_abx = read_tsv('tables/claims_by_abx.tsv')

n_million_bene = totals %$% unique(n_bene) %>% { round(. / 1e6, 1) }
n_million_pde = claims_by_abx %$% sum(n) %>% { round(. / 1e6, 1) }

est2pct = function(x) (exp(x) - 1)*100
model_ci = function(df) {
  df %>%
    filter(model=='poisson', term=='year') %>%
    mutate(pct_change=est2pct(estimate),
           ci=1.96*std.error,
           ci_low=est2pct(estimate - ci),
           ci_high=est2pct(estimate + ci),
           change_str=sprintf('%.2f%% (%.2f--%.2f%%)', pct_change, ci_low, ci_high))
}

model_abx = read_tsv('tables/model_abx.tsv') %>%
  model_ci()

total_adjusted_change_str = model_abx %>%
  filter(antibiotic=='overall') %$%
  change_str

azithro_adjusted_change_str = model_abx %>%
  filter(antibiotic=='azithromycin') %$%
  change_str

levo_adjusted_change_str = model_abx %>%
  filter(antibiotic=='levofloxacin') %$%
  change_str
```

There are `r n_million_bene` million beneficiaries and `r n_million_pde` million PDEs. Adjusted total consumption changed by `r total_adjusted_change_str`. Azithromycin changed by `r azithro_adjusted_change_str`. Levofloxacin changed by `r levo_adjusted_change_str`.

# Beneficiary characteristics

@@

A star indicates that the trend (*t*-test for mean difference between years equal to zero) is significant after multiple hypothesis correction.

```{r bene_char_table}
trend_p = function(x) tidy(t.test(diff(x)))$p.value
totals_trends = totals %>%
  gather('var', 'val', -year) %>%
  arrange(var, year, val) %>%
  group_by(var) %>%
  summarize(p=trend_p(val)) %>%
  mutate(adj.p=p.adjust(p, method='BH')) %>%
  mutate(sig=case_when(.$adj.p < 0.05 ~ '*',
                       .$p < 0.05 ~ '.',
                       TRUE ~ ''))

totals %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, sd_age, mean_n_cc, sd_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1)) %>%
  mutate_at(vars(mean_n_cc, sd_age, sd_n_cc),
            function(x) round(x, digits=2)) %>% 
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  left_join(totals_trends %>% select(var, sig), by='var') %>%
  kable
```

@@

```{r claims_by_abx}
top_abx = claims_by_abx %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

# this should be the same list as for the models
stopifnot(all(top_abx %in% model_abx$antibiotic))

# but "overall" should not be in the claims_by_abx list
if('overall' %in% claims_by_abx$antibiotic) stop()

claims_overall = claims_by_abx %>%
  select(-n_bene) %>%
  group_by(year) %>%
  summarize_at(vars(n, cpkp), sum) %>%
  mutate(antibiotic='overall')

claims_by_top_abx = claims_by_abx %>%
  bind_rows(claims_overall) %>%
  mutate(antibiotic=fct_relevel(fct_other(antibiotic, keep=c('overall', top_abx)),
                                c('overall', top_abx, 'Other'))) %>%
  group_by(year, antibiotic) %>%
  summarize_at(vars(n, cpkp), sum) %>% ungroup()

claims_by_top_abx %>%
  ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption')

claims_by_top_abx %>%
  filter(antibiotic != 'overall') %>%
  ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~antibiotic, ncol=3) +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption')

claims_by_top_abx %>%
  select(year, antibiotic, cpkp) %>%
  filter(year %in% c(2011, 2014)) %>%
  spread(year, cpkp) %>%
  mutate(pct_change=(`2014`-`2011`)/`2011`*100) %>%
  kable
```

@@

```{r claims_by_sex}
read_tsv('tables/claims_by_sex.tsv') %>%
  select(sex, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-sex), round) %>%
  kable
```

@@

```{r claims_by_region}
read_tsv('tables/claims_by_region.tsv') %>%
  select(region, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-region), round) %>%
  kable
```

@@

```{r claims_by_race}
read_tsv('tables/claims_by_race.tsv') %>%
  select(race, year, cpkp) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>% 
  mutate_at(vars(-race), round) %>%
  kable
```

@@

```{r adjusted_changes, cache.extra=md5sum('tables/model_abx.tsv')}
x = model_abx %>%
  filter(term=='year') %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  mutate(is_overall=antibiotic=='overall') %>%
  arrange(is_overall, pct_change) %>%
  mutate(antibiotic=fct_inorder(antibiotic)) %>%
  select(-is_overall)

x %>%
  ggplot(aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_point() +
  geom_linerange() +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  xlab('') +
  ylab('adjusted yearly change in claims per beneficiary per year') +
  #scale_y_continuous(limits=c(-16, 17), breaks=c(-15, -10, -5, 0, 5, 10, 15)) +
  theme_minimal()
```

```{r adjusted_changes_table}
x %>% arrange(-row_number()) %>% kable
```
